Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-23 Docs/TODAES/paper.tex
fix formulas
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>
fix references
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

\vspace{3 mm}
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $15$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$GB of memory.

@@

To perform the experiments, some benchmarks provided by Mann {\it et al.}~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}. The nodes in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area. The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}. The clustering and fuzzy benchmarks are designed from Mann {\it et al.}~\cite{Mann2007} and are significantly large benchmarks. From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).

@@

Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, Pavlinovic {\it et al.}~\cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by Pavlinovic {\it et al.}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.

>>>>

\vspace{3 mm}
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $15$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$ GB of memory.

@@

To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}. The nodes in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area. The first three benchmarks are extracted from MiBench~\cite{Guthaus2001}. The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks. From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).

@@

Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by \cite{Pavlinovic2015}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.
